%%% Thesis Introduction --------------------------------------------------
\renewcommand{\chaptername}{}
\chapter{Introduction}
\ifpdf
    \graphicspath{{Introduction/IntroductionFigs/PNG/}{Introduction/IntroductionFigs/PDF/}{Introduction/IntroductionFigs/}}
\else
    \graphicspath{{Introduction/IntroductionFigs/EPS/}{Introduction/IntroductionFigs/}}
\fi

Natural selection is the part of evolution where the fittest individual fixated 
Since 20th century this process has been explained in mathematical terms.
Two different models has been used to describe the dynamics of selection, the deterministic model and the stochastic model 
This stochastic simulations, has stochasticity due to the environment where the individuals are reproducing, but there is oder level of stochasticity due to internal gene expression noise.
The behavior of an individual also leads a fitness contribution.

Mathematics have created models for natural selection. this models then were change to stochastic models, functions of fitness or reproductive contribution of each organisms. This reproductive capacity(fitness) depends on a phenotype, that can be a physical advantage or social behavior in its biological system.
Usually this models considered the stochastic events external to organisms, these are for example changes in environment conditions on resources. These standard stochastic models do not consider internal stochastic events inside organism, which is responsible  of phenotypic variability in isogenic populations, the offspring is not an exact copy of its parent and have different whit the members of its generation. This is also transited to phenotypes related to social behaviors, as cooperate. Usually the models for evolution of altruism consider a discrete binary system of cooperation, where each  individual that cooperate,  do it at a fixed degree, but in real biological an human systems, individuals cooperate at different degrees.  



%%% ----------------------------------------------------------------------


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End: 
